### 2015-07-15 scyllarus-and-mifd.tex
Remove completed FIXME.
Clean a \cite that had the same reference repeated twice
i.e. \cite{xyz,xyz} ===> \cite{xyz}

Also squash some commas.

Our original system Scyllarus
%% TODO Restore for QR'15
% was an open system which 
performed IDS
fusion on a diverse set of third party \idses~\anoncite{goldman:discex2001,goldman:discex2001}.
Its successor,
MIFD (Model-based Intrusion Fusion and Detection),
enhances Scyllarus
%% TODO Restore for QR'15
% as part of the STRATUS system's integration of
 to integrate
IDS fusion into a comprehensive suite for cyber defense
\anoncite{thayer13:_compar_strat_tactic_respon_cyber_threat}.
For simplicity we refer to our \ids fusion system as ``MIFD,'' but
except where we specify otherwise, our account applies to Scyllarus as well.

@@

Figure \ref{fig:bnets}(a) shows the Bayes net generated by MIFD for
the very simple case of a single event hypothesized to be the cause of
a number of sensor reports.  In general sensor reports will be
ambiguous, each supporting several different event hypotheses.
Figure~\ref{fig:bnets}(b) shows a more complex example where sensor reports
might be caused by two different underlying events.
%% DONE: cut the following sentence because its meaning wasn't
%% clear.... I think what's meant is something like "label" rather than
%% "measurement," but I couldn't figure out how to clarify it. --- How
%% about this?
% The sensors themselves are simply either on or off, without any additional
% outputs which would distinguish hypotheses.

\ids rules detect indirect features of intrusions, but they typically
report only the intrusion that their designer believes has caused the feature.
This creates a number of problems, first and foremost that the
sensors have high false positive rates.
For example, a local software update server
may look like an attacker performing reconnaissance.
Worse, some false positives are correlated: the normal
activity of a print server may be mis-detected as a scan by several
different sensors.
To handle simple sensor failures, MIFD associates with each sensor a false
positive likelihood.
But to address the correlated false positives such as the scanning example, we
introduce benign events, that can compete with attack and (simple) false
positive explanations for results.\footnote{Where possible, we try to introduce sensors that
can specifically detect the benign events. 
%% TODO Restore for QR'15
%To return to our earlier example, we
%might introduce a ``print server sensor'' to help disambiguate detections. We do
%not address this issue in our experiments.
}
% FIXME: Add a figure 2(c) -- or separately numbered figure -- where we have a
% benign event, explaining two of the sensor reports, as well as the two attack
% events. 
Another problem with indirect sensing is that the sensors are often imprecise:
the features that they detect often occur not only in the absence of the
advertised intrusion, but in the presence of \emph{other} intrusions with
similar characteristics.

@@

\begin{figure}
  \centering
  \begin{tabular}{c@{\hspace{1cm}}c}
  \includegraphics[width=.2\columnwidth]{figures/bnets1-cropped.pdf} &
  \includegraphics[width=.267\columnwidth]{figures/bnets2-cropped.pdf} 
  \\ (a) & (b)
  \end{tabular}
  \caption{Bayes networks generated by MIFD.}
  \label{fig:bnets}
\end{figure}

>>>>

Our original system Scyllarus
%% TODO Restore for QR'15
% was an open system which 
performed IDS
fusion on a diverse set of third party \idses~\cite{goldman:discex2001}.
Its successor
MIFD (Model-based Intrusion Fusion and Detection)
enhances Scyllarus
%% TODO Restore for QR'15
% as part of the STRATUS system's integration of
 to integrate
IDS fusion into a comprehensive suite for cyber defense
\anoncite{thayer13:_compar_strat_tactic_respon_cyber_threat}.
For simplicity we refer to our \ids fusion system as ``MIFD,'' but
except where we specify otherwise, our account applies to Scyllarus as well.

@@

Figure \ref{fig:bnets}(a) shows the Bayes net generated by MIFD for
the very simple case of a single event hypothesized to be the cause of
a number of sensor reports.  In general sensor reports will be
ambiguous, each supporting several different event hypotheses.
Figure~\ref{fig:bnets}(b) shows a more complex example where sensor reports
might be caused by two different underlying events.
Finally, Figure~\ref{fig:bnets}(c) shows a more complex example where an event
has two component sub-events.
%% DONE: cut the following sentence because its meaning wasn't
%% clear.... I think what's meant is something like "label" rather than
%% "measurement," but I couldn't figure out how to clarify it. --- How
%% about this?
% The sensors themselves are simply either on or off, without any additional
% outputs which would distinguish hypotheses.

\ids rules detect indirect features of intrusions, but they typically
report only the intrusion that their designer believes has caused the feature.
This creates a number of problems, first and foremost that the
sensors have high false positive rates.
For example, a local software update server
may look like an attacker performing reconnaissance.
Worse, some false positives are correlated: the normal
activity of a print server may be mis-detected as a scan by several
different sensors.
To handle simple sensor failures, MIFD associates with each sensor a false
positive likelihood.
But to address the correlated false positives such as the scanning example, we
introduce benign events, that can compete with attack and (simple) false
positive explanations for results.\footnote{Where possible, we try to introduce sensors that
can specifically detect the benign events. 
%% TODO Restore for QR'15
%To return to our earlier example, we
%might introduce a ``print server sensor'' to help disambiguate detections. We do
%not address this issue in our experiments.
}

Another problem with indirect sensing is that the sensors are often imprecise:
the features that they detect often occur not only in the absence of the
advertised intrusion, but in the presence of \emph{other} intrusions with
similar characteristics.

@@

\begin{figure}
  \centering
  \begin{tabular}{c@{\hspace{1cm}}c}
  \includegraphics[width=.2\columnwidth]{figures/bnets1-cropped.pdf} &
  \includegraphics[width=.267\columnwidth]{figures/bnets2-cropped.pdf} 
  \\ (a) & (b) \\
  \end{tabular}
  \newline{}
  \begin{tabular}{c}
  \includegraphics[width=.4\columnwidth]{figures/bnets3-cropped.pdf} 
    \\ (c)
  \end{tabular}
  \caption{Bayes networks generated by MIFD.}
  \label{fig:bnets}

\end{figure}
